Introducing an event-based architecture for concurrent and distributed evolutionary algorithms

### 2018-05-29 paper.tex
Changes ref refs #2
Changes metadata

\title{A modern, event-based architecture for distributed evolutionary algorithms}
\titlerunning{A modern, event-based architecture for distributed EAs}

@@

%
\authorrunning{Garc\'ia-Valdez, Merelo Guerv\'os}

>>>>

\title{Introducing an event-based architecture for concurrent and distributed evolutionary algorithms}
\titlerunning{Introducing an event-based architecture for concurrent and distributed evolutionary algorithm}

@@

%
\authorrunning{Merelo Guerv\'os, Garc\'ia-Valdez}
